Lifting CDCL to Numerical Domains

### 2016-10-11 example.tex
minor

Hence, ACDCL makes an arbitrary decision $x:[-\infty,1]$ to refine the analysis.  
The decision constrains the interval of $x$.  The deductions made during fixed point
iteration are represented by abstract conflict graph in right-side of 
Figure~\ref{fig:example}.   Nodes in the graph denotes the corresponding 
updates to the program variables in the cfg.  Interval analysis concludes 
that the $(n12:\bot)$, that is the decision $x:[-\infty,1]$ leads to a 
{\em conflict}. Intuitively, it means that the program is {\em safe} for 
$x:[-\infty,1]$.

@@

The result of the analysis using ACDCL is shown in Figure~\ref{example}.  
Compared to a SAT solver, ACDCL makes only a single decision which lead 
to 240 interval constraint propagations, and learns a single conflict clause 
involving only one literal.  Compared to abstract interpretation, ACDCL does 
not require external hints to proof the program, thus automatically performing 
program and property driven trace partitioning to generate proofs using decision 
and clause learning.

>>>>

Hence, ACDCL makes an arbitrary decision $x:[-\infty,1]$ to refine the analysis.  
The decision constrains the interval of $x$.  The deductions made during fixed point
iteration are represented by abstract conflict graph in right-side of 
figure~\ref{example}.   Nodes in the graph denotes the corresponding 
updates to the program variables in the cfg.  Interval analysis concludes 
that the $(n12:\bot)$, that is the decision $x:[-\infty,1]$ leads to a 
{\em conflict}. Intuitively, it means that the program is {\em safe} for 
$x:[-\infty,1]$.

@@

The result of the analysis using ACDCL is shown in table~\ref{solver}.  
Compared to a SAT solver, ACDCL makes only a single decision which lead 
to 23 interval constraint propagations, and learns a single conflict clause 
involving only one literal.  Compared to abstract interpretation, ACDCL does 
not require external hints to proof the program, thus automatically performing 
program and property driven trace partitioning to generate proofs using decision 
and clause learning.
